---
title: "Simple ensemble build"
author: "Nicholas G Reich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple ensemble build}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  comment = "#>"
)
```

This vignette attempts to provide a minimal working example for building an ensemble using the `covidHubUtils` and `hubEnsembles` packages.

```{r}
library(covidHubUtils)
library(hubEnsembles)
library(dplyr)
```


## Loading forecasts

We start by loading some forecasts of weekly incident deaths from selected models. Note that these forecasts are retrieved from the US COVID-19 Forecast Hub data stored in the [Zoltar database](https://zoltardata.com/project/44) (the default specifications for the `load_forecasts()` function. 

```{r}
models = c("UMass-MechBayes", "USC-SI_kJalpha", "MOBS-GLEAM_COVID", "JHU_CSSE-DECOM", "CU-select", "BPagano-RtDriven")
forecast_data <- load_forecasts(
  models = models,
  targets = c(paste(1:4, "wk ahead inc death")),
  dates = "2021-12-20",
  date_window_size = 6,
  locations = c("US", "06"),
  types = "quantile")
```

We can plot these forecasts individually. If you are going to be making multiple forecast plots, it can speed things up to download truth data first.
```{r, fig.width=8, fig.height=4}
truth_data <- load_truth(
  truth_source = "JHU", 
  target_variable = "inc death", 
  locations = unique(forecast_data$location)
  )

plot_forecasts(
  forecast_data = forecast_data,
  facet = .~location,
  facet_scales = "free_y",
  truth_data = truth_data %>% filter(target_end_date > "2021-06-01"),
  truth_source = "JHU",
  use_median_as_point = TRUE, 
  fill_by_model = TRUE, 
  show_caption = FALSE, 
  fill_transparency = .3
  ) 
```


## Build ensemble

Next we build a simple average ensemble of all the models

```{r}
ensemble_forecast <- build_quantile_ensemble(forecast_data, 
                                             method = "median",
                                             forecast_date = "2021-12-20",
                                             model_name = "myTeam-ensemble",
                                             location_data = hub_locations)
```
 
and plot it 
```{r, fig.width=8, fig.height=4}
plot_forecasts(
  forecast_data = ensemble_forecast,
  facet = .~location,
  facet_scales = "free_y",
  truth_data = truth_data %>% filter(target_end_date > "2021-06-01"),
  truth_source = "JHU", 
  use_median_as_point = TRUE
  )
```




